### 2020-02-29 Thesis-Chapter3-Arguments.tex
Initial stab at building and including Argdown maps
Improve Argdown build process and image imports

In this chapter, develop the arguments introduced in \ref{sec-argsbackground}. Make use of argument maps to break down
and visualize the debate.

>>>>

In this chapter, develop the arguments introduced in \ref{sec-argsbackground}. Make use of argument maps to break down
and visualize the debate, as shown in \Figure~\fref{fig-args-top-level}.

% \includepdf[]{arguments/build/top-level.pdf}
\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=\linewidth]{arguments/build/top-level.pdf}
    \caption[Argument: Top Level]{Top level arguments for and against exceptional access.}
    \label{fig-args-top-level}
\end{figure}
